---
title: "Logistic Regression"
author: "Kathryn Gadberry"
date: "June 5, 2016"
output: html_document
---
## Example: National Health Interview Survey 

 Load and Review National Health Survey Data.
```{r}
setwd("/Users/kathryngadberry/Desktop/DATA COURSE/EDA/Regressions/logistic_regression 2")
NH11 <- readRDS("dataSets/NatHealth2011.rds")
labs <- attributes(NH11)$labels
str(NH11$hypev)
levels(NH11$hypev)

# Collapse all missing values and run Regression Model
NH11$hypev <- factor(NH11$hypev, levels = c("2 No", "1 Yes"))
hyp.out <- glm(hypev ~ age_p + sex + sleep + bmi, data = NH11, family = "binomial")
coef(summary(hyp.out))


# Transform the coefficients to better interpret the data (take out log odds)
hyp.out.tab <- coef(summary(hyp.out))
hyp.out.tab[, "Estimate"] <- exp(coef(hyp.out))
hyp.out.tab

```

Generating Predictive Values: How much more likely is a 63 year old female likely to have hypertension compared to a 33 year old female?
```{r}

predDat <- with(NH11, expand.grid(age_p = c (33, 63),
                 sex = "2 Female",
                 bmi = mean(bmi, na.rm = TRUE),
                 sleep = mean(sleep, na.rm = TRUE)))


cbind(predDat, predict(hyp.out, type = "response",
                         se.fit = TRUE, interval = "confidence",
                         newdata = predDat))
```

This tells us that a 33 year old female has a 13% probability of having been diagnosed with hypertension, while and 63 year old female has a 48% probability of having been diagnosed.

```{r}
# Compute and graph the predicted values
suppressMessages(library(dplyr))
suppressMessages(library(tidyr))
suppressMessages(library(Zelig))
suppressMessages(library(effects))

plot(allEffects(hyp.out))
```
 
## Exercise: Logistic Regression

1. Use glm to conduct a logistic regression to predict ever worked (everwrk) using age (age_ p) and marital status  (r_maritl).

```{r}
# Review the observations and variables
str(NH11)

# Clean up Ever worked NA observations
NH11$everwrk <- factor(NH11$everwrk, levels = c("2 No", "1 Yes"))

NH11_log <- glm(NH11$everwrk ~ age_p + r_maritl, data = NH11, family = binomial)
coef(summary(NH11_log))
``` 

2. Predict the probability of working for each level of marital status.
```{r}
levels(NH11$r_maritl)
prob.work.maritl <- factor(NH11$r_maritl, levels = c("0 Under 14 years", "1 Married - spouse in household", "2 Married - spouse not in household", "3 Married - spouse in household unknown", "4 Widowed", "5 Divorced", "6 Separated", "7 Never married", "8 Living with partner", "9 Unknown marital status"))
prob.work.maritl <- glm(everwrk ~ r_maritl, data = NH11, family = "binomial")
coef(summary(prob.work.maritl))
```
