---
title: "Linear Regression"
author: "Kathryn Gadberry"
date: "May 28, 2016"
output: html_document
---
# State Voting Model 
```{r}
getwd()
list.files() 
list.files("dataSets")
```

```{r}
states.data <- readRDS("dataSets/states.rds")
states.info <- data.frame(attributes(states.data)[c("names", "var.labels")])
tail(states.info, 8)
```

```{r}
sts.ex.sat <-subset(states.data, select = c("expense", "csat"))
summary(sts.ex.sat)
``` 


```{r}
cor(sts.ex.sat)
```


```{r}
plot(sts.ex.sat)
```

```{r}
sat.mod <-lm(csat ~ expense, data = states.data)
summary(sat.mod)
```

```{r}
summary(lm(csat ~ expense + percent, data = states.data))
class(sat.mod)
confint(sat.mod)
```

```{r}
hist(residuals(sat.mod))
par(mar = c(4, 4, 2, 2), mfrow = c(1,2))
plot(sat.mod, which = c(1, 2))
```

Comparing Voting Models

```{r}
sat.voting.mod <- lm(csat ~ expense + house +senate, data = na.omit(states.data))
sat.mod <- update(sat.mod, data = na.omit(states.data))
anova(sat.mod, sat.voting.mod)
coef(summary(sat.voting.mod))
```

Modeling Interaction
```{r}
sat.expense.by.percent <- lm(csat ~expense*income, data = states.data)
coef(summary(sat.expense.by.percent))
```

Regression with Categorical Predictors
```{r}
str(states.data$region)
states.data$region <- factor(states.data$region)
sat.region <- lm(csat ~ region,
                 data=states.data) 
coef(summary(sat.region)) 
anova(sat.region) 
``` 
 
 Reference Groups and Contrasts
```{r}
contrasts(states.data$region)
# change the reference group
coef(summary(lm(csat ~ C(region, base=4),
                data=states.data)))
# change the coding scheme
coef(summary(lm(csat ~ C(region, contr.helmert),
                data=states.data)))
```


# Exercise One: Least Squares Regression
Review data for fitting. 
```{r}
states.info
sts.en.met <- subset(states.data, select = c("metro", "energy"))
summary(sts.en.met)
cor(sts.en.met)
plot(sts.en.met)
```

Remove Missing Data
```{r}
is.na(sts.en.met)
sts.en.met <- na.omit(sts.en.met)
cor(sts.en.met)
```

Create and Interpret Model Summary
```{r}
energy.mod <- lm(energy ~ metro, data = states.data)
summary(energy.mod)
summary(lm(energy ~ metro, data = states.data))
```

Examine the model objects and use function methods. More info about fit.
```{r}
class(energy.mod)
names(energy.mod)
methods(class = class(energy.mod))[1:9]
```

```{r}
confint(energy.mod)
hist(residuals(energy.mod))
```

Plot the Model. 
```{r}
par(mar = c(4, 4, 2, 2), mfrow = c(1, 2)) 
plot(energy.mod, which = c(1, 2))
```

Adding variables to model: Metro, Miles, Density, Area, Population
```{r}
energy.mod1 <- lm(energy ~ metro + miles + density + area + pop, data = states.data)
summary(energy.mod1)
#Remove Density from variables
energy.mod2 <- lm(energy ~ metro + miles + area + pop, data = states.data)
summary(energy.mod2)
#Both R squared and Adjusted R squared increased
```
The adjusted R2 decreases with any variation from Model 2 
```{r}
energy.mod3 <-lm(energy ~ metro + miles + area, data = states.data)
summary(energy.mod3)

energy.mod4 <- lm(energy ~ miles + area + pop, data = states.data)
summary(energy.mod4)

energy.mod4 <- lm(energy ~ miles + area, data = states.data)
summary(energy.mod4)
``` 


# Exercise 2: Interactions and Factors

Add and test an interaction term.
```{r}
energy.metro.by.green <- lm(energy ~ metro*green, data = states.data)
coef(summary(energy.metro.by.green))
summary(energy.metro.by.green)
``` 

Test regression with categorical predictors by adding region. 
```{r}
str(states.data$region)
states.data$region <- factor(states.data$region)
energy.region <- lm(energy ~ metro + region,
                 data=states.data) 


summary(energy.region)
coef(summary(energy.region)) 
anova(energy.region) 
```  
